The Changing Face of Pediatric Pulmonary Exacerbations in CF (NACFC 2023)

### 2023-10-05 Scott Sagel/PEx in CF/nacfc_2023.qmd
nacfc presentation for Mo

chco <- read_excel("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Scott Sagel/PEx in CF/Data_Clean/CHCO.xlsx", na = c("", "NULL"))
cnh <- read_excel("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Scott Sagel/PEx in CF/Data_Clean/CNH.xlsx")

@@

write.csv(df,file = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Scott Sagel/PEx in CF/Data_Clean/pex_merged.csv",row.names = F,na = "")

@@

>>>>

chco <- read_excel("/Users/timvigers/Documents/Work/Vigers/CF/Scott Sagel/PEx in CF/Data_Clean/CHCO.xlsx", na = c("", "NULL"))
cnh <- read_excel("/Users/timvigers/Documents/Work/Vigers/CF/Scott Sagel/PEx in CF/Data_Clean/CNH.xlsx")

@@

write.csv(df, file = "/Users/timvigers/Documents/Work/Vigers/CF/Scott Sagel/PEx in CF/Data_Clean/pex_merged.csv", row.names = F, na = "")

@@

# Import REDCap data from Eli
data = read.csv("~/Documents/Work/Vigers/CF/Scott Sagel/PEx in CF/Data_Raw/ExacerbationsInCF222_DATA_2023-10-04_1459.csv",na.strings = "")
# Demographics
demo = data %>% filter(redcap_event_name == "demographics_arm_1")
